\documentclass{article}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}
\usepackage{Sweave}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage[small]{caption}
\usepackage{gensymb}
\usepackage{float}
\usepackage{url}
\setkeys{Gin}{width=0.8\textwidth}
\setlength{\captionmargin}{30pt}
\setlength{\abovecaptionskip}{0pt}
\setlength{\belowcaptionskip}{10pt}
\topmargin -1.5cm        
\oddsidemargin -0.04cm   
\evensidemargin -0.04cm
\textwidth 16.59cm
\textheight 21.94cm 
\pagestyle{empty}
\parskip 7.2pt
\renewcommand{\baselinestretch}{1.5}
\parindent 0pt
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

\renewcommand{\thetable}{\arabic{table}}
\renewcommand{\thefigure}{\arabic{figure}}
\renewcommand{\labelitemi}{$-$}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Prioritized List}
\author{Suzanne Mrozak, Danny Schissler, Cat Chamberlain}
\date{\today}
\maketitle
\section*{AIM}
The goal of this document is to formulate a prioritized task list to be completed before the fall. This is our two month plan. The next step is to establish a 4-6 month plan and then a one year plan. 
\section*{TO DO ASAP}
\begin{enumerate}
\item Review the goals of the program
\begin{enumerate}
  \item Mission Statement: 1 Year Plan
  \item Vision Statement: 3-5 Year Plan
\end{enumerate}
\item Review communication options and determine our approach. Consolidate our current resources -- Arb website, Facebook, Meetup, Temporal Ecology lab site, Flickr, Google, Twitter. Should we make a new website, affiliated with the Temporal Ecology site but one that has our own logo and design in an effort to transition to become more strongly associated with the Arboretum?
\item We need a better way to distribute Spot On! and in general, a more efficient way to contact all Tree Spotters. Adjust Tree Spotters email address and system. 
\item Contact NPN about doing a presentation for the annual NPN partners' showcase
\item Review and revise basic training lsides. Create a fall and spring version, with fall training being the immediate priority. 
\begin{enumerate}
  \item What are we doing with the data? How do we communicate this to the Tree Spotters in a more approachable manner?
\end{enumerate}
\item Develop additional training and support materials
\begin{enumerate}
  \item How to use your NPN Observation Deck
  \item What you can do with the data
  \item Online Focus Tree Notebook -- Biggest Priority! 
  \item Updated guides that covers all of the phenophases for each tree 
\end{enumerate}
\end{enumerate}
\section*{PROGRESS}
We have started working on establishing both a Mission and Vision Statement. We are in the process of desiging a new training regime and program. Next week, Suz will be meeting with volunteers to start working on a prototype for the Focus Tree Notebook. We understand that we are still in pilote mode but we are working hard to transition out of that phase and into more stability. 


\end{document}
